\documentclass[11pt,letterpaper]{article}
\usepackage[margin=1in]{geometry}
\usepackage{fancyhdr}
\usepackage{xcolor}
\usepackage{tikz}
\usepackage{enumitem}
\usepackage{tcolorbox}
\usepackage{tabularx}

% Define colors
\definecolor{maincolor}{RGB}{102,187,106}
\definecolor{lightgray}{RGB}{245,245,245}

% Header and footer
\pagestyle{fancy}
\fancyhf{}
\fancyhead[L]{\textcolor{maincolor}{\textbf{PSIS 4700: Applied AI}}}
\fancyhead[R]{\textcolor{gray}{Worksheet}}
\fancyfoot[C]{\thepage}
\renewcommand{\headrulewidth}{2pt}
\renewcommand{\footrulewidth}{0pt}

% Custom section formatting
\usepackage{titlesec}
\titleformat{\section}{\Large\bfseries\color{maincolor}}{\thesection}{1em}{}
\titleformat{\subsection}{\large\bfseries\color{maincolor}}{\thesubsection}{1em}{}

% Custom box for fill-in sections
\newtcolorbox{fillbox}[1][]{
  colback=lightgray,
  colframe=maincolor,
  boxrule=1pt,
  arc=3pt,
  left=10pt,
  right=10pt,
  top=15pt,
  bottom=15pt,
  #1
}

\setlength{\parindent}{0pt}
\setlength{\parskip}{10pt}

\begin{document}

% Title
\begin{center}
    \textcolor{maincolor}{\rule{\textwidth}{2pt}}
    \vspace{10pt}
    
    {\Huge\bfseries AI Workflow Quick Guide}
    
    \vspace{5pt}
    {\large Consistent Practice for Reliable Results}
    
    \vspace{10pt}
    \textcolor{maincolor}{\rule{\textwidth}{2pt}}
\end{center}

\vspace{20pt}

\section*{Purpose}

This guide shows the full AI workflow in plain steps. The goal is consistent practice and reliable results.

\vspace{15pt}

\section*{Step 1. Define the Goal}

State the problem in one sentence. State what a good result looks like.

\begin{fillbox}[title=\textbf{Goal:}]
\vspace{40pt}
\end{fillbox}

\begin{fillbox}[title=\textbf{Outcome:}]
\vspace{40pt}
\end{fillbox}

\section*{Step 2. Prepare the Input}

Describe the information the model will use. Confirm clarity and relevance.

\begin{fillbox}[title=\textbf{Input:}]
\vspace{40pt}
\end{fillbox}

\begin{fillbox}[title=\textbf{Context:}]
\vspace{40pt}
\end{fillbox}

\section*{Step 3. Write the First Prompt}

Give clear instructions. State structure, tone, and format.

\begin{fillbox}[title=\textbf{Prompt:}]
\vspace{60pt}
\end{fillbox}

\begin{fillbox}[title=\textbf{Output:}]
\vspace{60pt}
\end{fillbox}

\newpage

\section*{Step 4. Review the Result}

Check accuracy, usefulness, and risk. Record strengths and weaknesses.

\begin{fillbox}[title=\textbf{Strengths:}]
\vspace{50pt}
\end{fillbox}

\begin{fillbox}[title=\textbf{Weaknesses:}]
\vspace{50pt}
\end{fillbox}

\section*{Step 5. Improve the Prompt}

Add clarity. Add structure. Add context.

\begin{fillbox}[title=\textbf{Revised Prompt:}]
\vspace{60pt}
\end{fillbox}

\begin{fillbox}[title=\textbf{New Output:}]
\vspace{60pt}
\end{fillbox}

\begin{fillbox}[title=\textbf{Difference Noticed:}]
\vspace{40pt}
\end{fillbox}

\section*{Step 6. Reflect and Record}

\begin{fillbox}[title=\textbf{What worked:}]
\vspace{40pt}
\end{fillbox}

\begin{fillbox}[title=\textbf{What changed:}]
\vspace{40pt}
\end{fillbox}

\begin{fillbox}[title=\textbf{What you would try next:}]
\vspace{40pt}
\end{fillbox}

\end{document}
