\documentclass[11pt,letterpaper]{article}
\usepackage[margin=0.75in]{geometry}
\usepackage{fancyhdr}
\usepackage{xcolor}
\usepackage{tikz}
\usepackage{enumitem}
\usepackage{tcolorbox}
\usepackage{tabularx}
\usepackage{array}
\usepackage{booktabs}
\usepackage{longtable}

% Define colors
\definecolor{maincolor}{RGB}{102,187,106}
\definecolor{lightgray}{RGB}{245,245,245}

% Header and footer
\pagestyle{fancy}
\fancyhf{}
\fancyhead[L]{\textcolor{maincolor}{\textbf{PSIS 4700: Applied AI}}}
\fancyhead[R]{\textcolor{gray}{Worksheet}}
\fancyfoot[C]{\thepage}
\renewcommand{\headrulewidth}{2pt}
\renewcommand{\footrulewidth}{0pt}

% Custom section formatting
\usepackage{titlesec}
\titleformat{\section}{\Large\bfseries\color{maincolor}}{\thesection}{1em}{}
\titleformat{\subsection}{\large\bfseries\color{maincolor}}{\thesubsection}{1em}{}

% Custom box for fill-in sections
\newtcolorbox{fillbox}[1][]{
  colback=lightgray,
  colframe=maincolor,
  boxrule=1pt,
  arc=3pt,
  left=10pt,
  right=10pt,
  top=15pt,
  bottom=15pt,
  #1
}

\setlength{\parindent}{0pt}
\setlength{\parskip}{8pt}

\begin{document}

% Title
\begin{center}
    \textcolor{maincolor}{\rule{\textwidth}{2pt}}
    \vspace{8pt}
    
    {\Huge\bfseries Applied AI Planning Pack}
    
    \vspace{4pt}
    {\large Project Ideas, Scoping, and Learning Path}
    
    \vspace{8pt}
    \textcolor{maincolor}{\rule{\textwidth}{2pt}}
\end{center}

\vspace{15pt}

\section*{Mini-Project Idea Bank}

Use these ideas as starting points. Pick one idea. Define the goal. Keep the scope small.

\vspace{10pt}

\small
\renewcommand{\arraystretch}{1.8}
\begin{longtable}{|p{3cm}|p{3.2cm}|p{2.3cm}|p{2.5cm}|p{2cm}|}
\hline
\rowcolor{lightgray}
\textbf{Idea Name} & \textbf{Short Description} & \textbf{Data Source} & \textbf{Expected Output} & \textbf{Time Required} \\
\hline
\endfirsthead
\hline
\rowcolor{lightgray}
\textbf{Idea Name} & \textbf{Short Description} & \textbf{Data Source} & \textbf{Expected Output} & \textbf{Time Required} \\
\hline
\endhead
Writing Assistant & Improve a draft and reduce errors & User text & Revised draft with edits & One hour \\
\hline
Email Classifier & Sort emails by topic & Sample email set & Labeled categories & One hour \\
\hline
Study Helper & Produce summaries from notes & Student notes & Short summaries & One hour \\
\hline
Task Prioritizer & Rank tasks by importance & Task list & Ordered task list & One hour \\
\hline
Meeting Notes Cleaner & Rewrite long notes for clarity & Raw transcript & Clean summary & One hour \\
\hline
Idea Generator & Produce options for a problem & Prompt text & Set of ideas & Thirty minutes \\
\hline
Policy Checker & Review a document for risks & Sample document & Risk checklist & One hour \\
\hline
Customer Question Helper & Suggest replies to questions & Question dataset & Draft responses & One hour \\
\hline
Lesson Outline Builder & Create teaching outlines & Topic prompt & Structured outline & One hour \\
\hline
Research Companion & Extract key points from articles & Article text & Key insights & One hour \\
\hline
\end{longtable}
\normalsize

\newpage

\section*{Project Scoping Template}

Use this template before you begin. Define the goal. Define success. Keep the work focused.

\subsection*{Project Title}

\begin{fillbox}[title=\textbf{Title:}]
\vspace{25pt}
\end{fillbox}

\subsection*{Problem Statement}
Describe the problem in one sentence.

\begin{fillbox}[title=\textbf{Problem:}]
\vspace{30pt}
\end{fillbox}

\subsection*{Outcome}
Describe what success looks like.

\begin{fillbox}[title=\textbf{Outcome:}]
\vspace{30pt}
\end{fillbox}

\subsection*{Input and Output}

\begin{fillbox}[title=\textbf{Input:}]
\vspace{30pt}
\end{fillbox}

\begin{fillbox}[title=\textbf{Output:}]
\vspace{30pt}
\end{fillbox}

\subsection*{Data}

\begin{fillbox}[title=\textbf{Data Source:}]
\vspace{30pt}
\end{fillbox}

\begin{fillbox}[title=\textbf{Data Limits:}]
\vspace{30pt}
\end{fillbox}

\newpage

\subsection*{Constraints}

\begin{fillbox}[title=\textbf{Constraints:}]
\vspace{30pt}
\end{fillbox}

\subsection*{Evaluation}

\begin{fillbox}[title=\textbf{Success Criteria:}]
\vspace{30pt}
\end{fillbox}

\begin{fillbox}[title=\textbf{Review Method:}]
\vspace{30pt}
\end{fillbox}

\subsection*{Risks}

\begin{fillbox}[title=\textbf{Risks:}]
\vspace{30pt}
\end{fillbox}

\begin{fillbox}[title=\textbf{Mitigation:}]
\vspace{30pt}
\end{fillbox}

\subsection*{Next Actions}

\begin{fillbox}[title=\textbf{First Action:}]
\vspace{25pt}
\end{fillbox}

\begin{fillbox}[title=\textbf{Second Action:}]
\vspace{25pt}
\end{fillbox}

\newpage

\section*{Learning Path Planner}

Use this planner to track progress. Focus on steady improvement. Keep goals realistic.

\subsection*{Current Skill Level}

\begin{fillbox}[title=\textbf{Strengths:}]
\vspace{30pt}
\end{fillbox}

\begin{fillbox}[title=\textbf{Gaps:}]
\vspace{30pt}
\end{fillbox}

\subsection*{Learning Goal}

\begin{fillbox}[title=\textbf{Goal:}]
\vspace{25pt}
\end{fillbox}

\begin{fillbox}[title=\textbf{Reason:}]
\vspace{25pt}
\end{fillbox}

\subsection*{Practice Plan}

Describe what you will practice and why it matters.

\vspace{10pt}

\renewcommand{\arraystretch}{2.5}
\begin{tabularx}{\textwidth}{|c|X|X|c|X|}
\hline
\rowcolor{lightgray}
\textbf{Week} & \textbf{Focus Area} & \textbf{Practice Task} & \textbf{Time Planned} & \textbf{Result} \\
\hline
 & & & & \\
\hline
 & & & & \\
\hline
 & & & & \\
\hline
 & & & & \\
\hline
\end{tabularx}

\vspace{15pt}

\subsection*{Reflection}

Record lessons learned after each cycle.

\begin{fillbox}[title=\textbf{What improved:}]
\vspace{30pt}
\end{fillbox}

\begin{fillbox}[title=\textbf{What stayed weak:}]
\vspace{30pt}
\end{fillbox}

\begin{fillbox}[title=\textbf{What to change next time:}]
\vspace{30pt}
\end{fillbox}

\subsection*{Next Step}

\begin{fillbox}[title=\textbf{Next Step:}]
\vspace{25pt}
\end{fillbox}

\begin{fillbox}[title=\textbf{Target Date:}]
\vspace{20pt}
\end{fillbox}

\end{document}
