\documentclass[11pt,letterpaper]{article}
\usepackage[margin=0.85in]{geometry}
\usepackage{fancyhdr}
\usepackage{xcolor}
\usepackage{tikz}
\usepackage{enumitem}
\usepackage{tcolorbox}
\usepackage{tabularx}

% Define colors
\definecolor{maincolor}{RGB}{102,187,106}
\definecolor{lightgray}{RGB}{245,245,245}

% Header and footer
\pagestyle{fancy}
\fancyhf{}
\fancyhead[L]{\textcolor{maincolor}{\textbf{PSIS 4700: Applied AI}}}
\fancyhead[R]{\textcolor{gray}{Worksheet}}
\fancyfoot[C]{\thepage}
\renewcommand{\headrulewidth}{2pt}
\renewcommand{\footrulewidth}{0pt}

% Custom section formatting
\usepackage{titlesec}
\titleformat{\section}{\Large\bfseries\color{maincolor}}{\thesection}{1em}{}
\titleformat{\subsection}{\large\bfseries\color{maincolor}}{\thesubsection}{1em}{}

% Custom box for fill-in sections
\newtcolorbox{fillbox}[1][]{
  colback=lightgray,
  colframe=maincolor,
  boxrule=1pt,
  arc=3pt,
  left=10pt,
  right=10pt,
  top=15pt,
  bottom=15pt,
  #1
}

\setlength{\parindent}{0pt}
\setlength{\parskip}{8pt}

\begin{document}

% Title
\begin{center}
    \textcolor{maincolor}{\rule{\textwidth}{2pt}}
    \vspace{8pt}
    
    {\Huge\bfseries GenAI Practice Pack}
    
    \vspace{4pt}
    {\large Planning, Testing, and Refining Generative AI Tasks}
    
    \vspace{8pt}
    \textcolor{maincolor}{\rule{\textwidth}{2pt}}
\end{center}

\vspace{15pt}

\section*{GenAI Task Planner}

Use this planner before you begin a task. Define the goal. Define the format. Plan the review.

\subsection*{Task}
Describe the task in one sentence.

\begin{fillbox}[title=\textbf{Task:}]
\vspace{25pt}
\end{fillbox}

\subsection*{Purpose}
Describe why the task matters.

\begin{fillbox}[title=\textbf{Purpose:}]
\vspace{25pt}
\end{fillbox}

\subsection*{Desired Outcome}
Describe what a good result looks like.

\begin{fillbox}[title=\textbf{Outcome:}]
\vspace{25pt}
\end{fillbox}

\subsection*{Audience}
Describe who will read or use the result.

\begin{fillbox}[title=\textbf{Audience:}]
\vspace{25pt}
\end{fillbox}

\subsection*{Input}
Describe what information the model will receive.

\begin{fillbox}[title=\textbf{Input:}]
\vspace{30pt}
\end{fillbox}

\subsection*{Output Format}

\begin{fillbox}[title=\textbf{Format:}]
\vspace{20pt}
\end{fillbox}

\begin{fillbox}[title=\textbf{Length:}]
\vspace{20pt}
\end{fillbox}

\begin{fillbox}[title=\textbf{Tone:}]
\vspace{20pt}
\end{fillbox}

\subsection*{Constraints}
Describe rules such as scope, time, or sensitivity.

\begin{fillbox}[title=\textbf{Constraints:}]
\vspace{30pt}
\end{fillbox}

\newpage

\subsection*{Risks}
Describe what could go wrong and how you will check it.

\begin{fillbox}[title=\textbf{Risks:}]
\vspace{30pt}
\end{fillbox}

\begin{fillbox}[title=\textbf{Review Steps:}]
\vspace{30pt}
\end{fillbox}

\subsection*{Success Check}
Describe how you will decide the result is acceptable.

\begin{fillbox}[title=\textbf{Acceptance Criteria:}]
\vspace{30pt}
\end{fillbox}

\begin{fillbox}[title=\textbf{Next Action if not acceptable:}]
\vspace{25pt}
\end{fillbox}

\vspace{20pt}

\section*{Prompt Refinement Guide}

Use this guide to improve weak outputs. Start with a draft. Add clarity. Add structure. Add context.

\subsection*{Step 1. First Attempt}

\begin{fillbox}[title=\textbf{Initial Prompt:}]
\vspace{40pt}
\end{fillbox}

\begin{fillbox}[title=\textbf{Model Output:}]
\vspace{40pt}
\end{fillbox}

\begin{fillbox}[title=\textbf{Strengths:}]
\vspace{25pt}
\end{fillbox}

\begin{fillbox}[title=\textbf{Weaknesses:}]
\vspace{25pt}
\end{fillbox}

\newpage

\subsection*{Step 2. Add Clarity}
State the goal again. Remove vague wording.

\begin{fillbox}[title=\textbf{Change made:}]
\vspace{30pt}
\end{fillbox}

\begin{fillbox}[title=\textbf{Revised Prompt:}]
\vspace{40pt}
\end{fillbox}

\begin{fillbox}[title=\textbf{Output:}]
\vspace{40pt}
\end{fillbox}

\begin{fillbox}[title=\textbf{Improvement observed:}]
\vspace{25pt}
\end{fillbox}

\subsection*{Step 3. Add Structure}
Name the format. Use examples.

\begin{fillbox}[title=\textbf{Change made:}]
\vspace{30pt}
\end{fillbox}

\begin{fillbox}[title=\textbf{Revised Prompt:}]
\vspace{40pt}
\end{fillbox}

\begin{fillbox}[title=\textbf{Output:}]
\vspace{40pt}
\end{fillbox}

\begin{fillbox}[title=\textbf{Improvement observed:}]
\vspace{25pt}
\end{fillbox}

\newpage

\subsection*{Step 4. Add Context}
Provide background or constraints.

\begin{fillbox}[title=\textbf{Change made:}]
\vspace{30pt}
\end{fillbox}

\begin{fillbox}[title=\textbf{Revised Prompt:}]
\vspace{40pt}
\end{fillbox}

\begin{fillbox}[title=\textbf{Output:}]
\vspace{40pt}
\end{fillbox}

\begin{fillbox}[title=\textbf{Improvement observed:}]
\vspace{25pt}
\end{fillbox}

\subsection*{Final Reflection}

\begin{fillbox}[title=\textbf{What helped most:}]
\vspace{30pt}
\end{fillbox}

\begin{fillbox}[title=\textbf{What patterns you will reuse:}]
\vspace{30pt}
\end{fillbox}

\begin{fillbox}[title=\textbf{What you would try next time:}]
\vspace{30pt}
\end{fillbox}

\end{document}
