\documentclass[11pt,letterpaper]{article}
\usepackage[margin=1in]{geometry}
\usepackage{fancyhdr}
\usepackage{xcolor}
\usepackage{tikz}
\usepackage{enumitem}
\usepackage{tcolorbox}
\usepackage{tabularx}

% Define colors
\definecolor{maincolor}{RGB}{102,187,106}
\definecolor{lightgray}{RGB}{245,245,245}
\definecolor{warningcolor}{RGB}{255,193,7}

% Header and footer
\pagestyle{fancy}
\fancyhf{}
\fancyhead[L]{\textcolor{maincolor}{\textbf{PSIS 4700: Applied AI}}}
\fancyhead[R]{\textcolor{gray}{Worksheet}}
\fancyfoot[C]{\thepage}
\renewcommand{\headrulewidth}{2pt}
\renewcommand{\footrulewidth}{0pt}

% Custom section formatting
\usepackage{titlesec}
\titleformat{\section}{\Large\bfseries\color{maincolor}}{\thesection}{1em}{}
\titleformat{\subsection}{\large\bfseries\color{maincolor}}{\thesubsection}{1em}{}

% Custom box for fill-in sections
\newtcolorbox{fillbox}[1][]{
  colback=lightgray,
  colframe=maincolor,
  boxrule=1pt,
  arc=3pt,
  left=10pt,
  right=10pt,
  top=15pt,
  bottom=15pt,
  #1
}

% Problem box
\newtcolorbox{problembox}[1][]{
  colback=white,
  colframe=warningcolor,
  boxrule=2pt,
  arc=3pt,
  left=10pt,
  right=10pt,
  top=10pt,
  bottom=10pt,
  #1
}

\setlength{\parindent}{0pt}
\setlength{\parskip}{10pt}

\begin{document}

% Title
\begin{center}
    \textcolor{maincolor}{\rule{\textwidth}{2pt}}
    \vspace{10pt}
    
    {\Huge\bfseries Prompt Troubleshooting Guide}
    
    \vspace{5pt}
    {\large Fixing Weak Prompts for Better Results}
    
    \vspace{10pt}
    \textcolor{maincolor}{\rule{\textwidth}{2pt}}
\end{center}

\vspace{20pt}

\section*{Purpose}

This guide helps you fix weak prompts and improve results.

\vspace{15pt}

\section*{Problem 1. Output Is Vague}

\begin{problembox}
\textbf{Cause:} Prompt lacks detail or context.

\textbf{Fix:} Add a clear goal. Add audience and format.
\end{problembox}

\begin{fillbox}[title=\textbf{Revised Prompt:}]
\vspace{60pt}
\end{fillbox}

\begin{fillbox}[title=\textbf{Result:}]
\vspace{40pt}
\end{fillbox}

\section*{Problem 2. Output Misses the Point}

\begin{problembox}
\textbf{Cause:} Prompt does not state what matters.

\textbf{Fix:} Name the key focus. State constraints.
\end{problembox}

\begin{fillbox}[title=\textbf{Revised Prompt:}]
\vspace{60pt}
\end{fillbox}

\begin{fillbox}[title=\textbf{Result:}]
\vspace{40pt}
\end{fillbox}

\newpage

\section*{Problem 3. Output Changes Tone}

\begin{problembox}
\textbf{Cause:} Prompt does not define style.

\textbf{Fix:} Describe tone. Provide a sample line.
\end{problembox}

\begin{fillbox}[title=\textbf{Revised Prompt:}]
\vspace{60pt}
\end{fillbox}

\begin{fillbox}[title=\textbf{Result:}]
\vspace{40pt}
\end{fillbox}

\section*{Problem 4. Output Includes Wrong Facts}

\begin{problembox}
\textbf{Cause:} Prompt encourages confident guessing.

\textbf{Fix:} Ask for uncertainty notes. Ask for citations or limits.
\end{problembox}

\begin{fillbox}[title=\textbf{Revised Prompt:}]
\vspace{60pt}
\end{fillbox}

\begin{fillbox}[title=\textbf{Result:}]
\vspace{40pt}
\end{fillbox}

\section*{Reflection}

\begin{fillbox}[title=\textbf{What fix worked best:}]
\vspace{40pt}
\end{fillbox}

\begin{fillbox}[title=\textbf{What pattern repeats:}]
\vspace{40pt}
\end{fillbox}

\begin{fillbox}[title=\textbf{What you will try next:}]
\vspace{40pt}
\end{fillbox}

\end{document}
