\documentclass[11pt,letterpaper]{article}
\usepackage[margin=0.75in]{geometry}
\usepackage{fancyhdr}
\usepackage{xcolor}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{multicol}

% Define colors
\definecolor{maincolor}{RGB}{33,150,243}
\definecolor{lightgray}{RGB}{245,245,245}

% Header and footer
\pagestyle{fancy}
\fancyhf{}
\fancyhead[L]{\textcolor{maincolor}{\textbf{PSIS 4700: Applied AI}}}
\fancyhead[R]{\textcolor{gray}{Reference Sheet}}
\fancyfoot[C]{\thepage}
\renewcommand{\headrulewidth}{2pt}
\renewcommand{\footrulewidth}{0pt}
\setlength{\headheight}{14pt}

% Custom section formatting
\titleformat{\section}{\large\bfseries\color{maincolor}}{\thesection}{1em}{}[\titlerule]
\titleformat{\subsection}{\normalsize\bfseries\color{maincolor}}{\thesubsection}{1em}{}

\setlength{\parindent}{0pt}
\setlength{\parskip}{8pt}
\setlist{nosep}

\begin{document}

% Title
\begin{center}
    \textcolor{maincolor}{\rule{\textwidth}{2pt}}
    \vspace{8pt}
    
    {\huge\bfseries AI Terms in Plain English}
    
    \vspace{5pt}
    {\normalsize Quick Reference Guide}
    
    \vspace{8pt}
    \textcolor{maincolor}{\rule{\textwidth}{2pt}}
\end{center}

\vspace{10pt}

\begin{multicols}{2}

\subsection*{Artificial Intelligence}
Artificial intelligence means software that performs tasks that normally require human judgment. The system takes input, applies a model, and produces an output such as text, a decision, or a prediction.

\subsection*{Model}
A model is a set of mathematical rules that connect inputs to outputs. The model follows patterns it learned from data and uses those patterns to answer new questions.

\subsection*{Training Data}
Training data is the set of examples the model studies before it produces results. Strong training data leads to better outputs. Weak training data leads to weak outputs.

\subsection*{Machine Learning}
Machine learning is a way to build models that learn patterns from data instead of using fixed rules written by a programmer.

\subsection*{Prediction}
A prediction is the model's best guess about a future value or an unknown value. The guess comes from patterns in past data.

\subsection*{Classification}
Classification means assigning a label to something. The model decides which category a case belongs to based on past examples.

\subsection*{Clustering}
Clustering means grouping similar things together. The model finds patterns that show which cases belong near each other.

\subsection*{Bias}
Bias means results that unfairly favor one group over another. Bias often comes from biased data or poor design choices.

\subsection*{Hallucination}
Hallucination means the model produces an answer that sounds correct but is not true. The model fills gaps instead of saying it does not know.

\subsection*{Large Language Model}
A large language model is a type of AI system that predicts the next word or token in a sequence based on patterns in text. The model does not understand meaning. It works through probability.

\subsection*{Generative AI}
Generative AI produces new text, images, audio, or code. The output looks original, but the model creates it from patterns in the data it studied.

\subsection*{Prompt}
A prompt is the instruction you give to the model. A clear prompt produces clearer results.

\subsection*{Prompt Refinement}
Prompt refinement means adjusting a prompt to improve the output. You change wording, add context, or set constraints to guide the model.

\subsection*{Evaluation}
Evaluation means checking whether the model produced a useful and correct result. People review outputs to confirm quality.

\subsection*{Human in the Loop}
Human in the loop means a person stays involved. The person sets the goal, checks the results, and decides what to accept or change.

\subsection*{Privacy}
Privacy means protecting personal or sensitive information. Good practice avoids exposing private data to AI systems.

\subsection*{Drift}
Drift means the world changes over time while the model stays the same. The model becomes less accurate because reality moved away from its training data.

\subsection*{Transparency}
Transparency means explaining how an AI system works at a level people can understand. The system should not feel like a hidden black box.

\subsection*{Accountability}
Accountability means people remain responsible for outcomes produced with AI. A tool does not replace human responsibility.

\end{multicols}

\end{document}
